---
title: "IPCC 2021"
author: "DS-SL"
date: "`r Sys.Date()`" 
output: 
  html_notebook:
#    number_sections: yes
#    toc: true
#    toc_float: true
---
# About

* [IPCC Sixth Assessment Report Working Group 1: The Physical Science Basis}(https://www.ipcc.ch/report/ar6/wg1/) 
	- Data: [The Physical Science Basis. Working Group I Contribution to the IPCC Sixth Assessment Report]( https://catalogue.ceda.ac.uk/uuid/3234e9111d4f4354af00c3aaecd879b7)
	- Code: [IPCC-WG1 Official GitHub repository for IPCC-WG1](https://github.com/IPCC-WG1)
	  + There are 106 repositories
	  + List of Popular Repositories
	    * Atlas: 168 forks
	    * Chapter 9: 11 forks
	    * colormaps: 9 forks
	    * Chapter 7: 6 forks
	    * Chapter 12: 5 forks
	    * tsu-colormaps: 1 fork
* Our World in Data: [Data Explorer: IPCC Scenarios](https://ourworldindata.org/explorers/ipcc-scenarios?facet=none&pickerSort=asc&pickerMetric=Entity&Metric=Greenhouse+gas+concentrations&Sub-metric=Carbon+dioxide+%28CO₂%29&Rate=Per+capita&Region=Asia&country=SSP1+-+1.9~SSP1+-+2.6~SSP1+-+3.4~SSP1+-+4.5~SSP1+-+Baseline)
  - Data and figures are available
	    
## IPCC Repositories
### Atlas

* [Repository](https://github.com/IPCC-WG1/Atlas): Repository supporting the implementation of FAIR principles in the IPCC-WGI Atlas
  - [IPCC WGI Interactive Atlas](https://interactive-atlas.ipcc.ch)
    + Regional Information
    + Regional Synthesis
    + Documentation

### Chapter 9

* [Repository](https://github.com/IPCC-WG1/Chapter-9#repository-with-the-code-and-data-for-all-figures-from-chapter-9-of-the-sixth-assesment-report-from-the-intergovernmental-panel-on-climate-change-ipcc-ar6): Repository with the code and data for all figures from Chapter 9 of the Sixth Assesment Report from the Intergovernmental Panel on Climate Change (IPCC AR6).

# Our World Data

## Setup

```{r}
library(tidyverse)
```

## IPCC Senarios

* Data Published by: Riahi et al. (2017). The Shared Socioeconomic Pathways and their energy, land use, and greenhouse gas emissions implications: An overview, Global Environmental Change
  + Source: https://tntcat.iiasa.ac.at/SspDb/dsd
  + Riahi, K., Van Vuuren, D. P., Kriegler, E., Edmonds, J., O’neill, B. C., Fujimori, S., … & Tavoni, M. (2017). The shared socioeconomic pathways and their energy, land use, and greenhouse gas emissions implications: an overview. Global environmental change, 42, 153-168
    - [Original Paper](https://www.sciencedirect.com/science/article/pii/S0959378016300681)
* What is the Shared Socioeconomic Pathways (SSPs)
* Five Summaries:
  + SSP1 provides the most positive scenario for both human development and environmental action. We continue to see improvements in education and health across the world; large reductions in poverty; and a shrinking in global inequalities. This is a scenario in which the researchers at the same time envision that the world is moving into a much more sustainable direction. 
  + SSP5 is similarly optimistic in terms of human development, but achieves this through a large growth in fossil fuels. This is therefore leading to continued large negative effects on the environment.
  + SSP3 and SSP4 are pessimistic about development: they envision a divided future with high levels of nationalism and large persistent global inequalities as a result. SSP2 sits in the middle of these scenarios: development is not as slow or divided as in SSP3 and SSP4, but progress is slow and unequal.

```{r}
df_owd1 <- read_csv("data/ipcc-scenarios.csv")
df_owd1
```

```{r}
colnames(df_owd1)
```

```{r}
df_owd1 %>% ggplot(aes(x = Year, y = `CO2 emissions`, color = Scenario)) + 
  geom_line()
```

