---
title: "World Inequality Report 2022"
author: "DS-SL"
date: "`r Sys.Date()`" 
output: 
  html_notebook:
    number_sections: yes
#    toc: true
#    toc_float: true
---

# Introduction

## WIR2022

* Executive Summary: https://wir2022.wid.world/executive-summary/
* Methodology: https://wir2022.wid.world/methodology/

# Executive Summary

## Setup

* Data: https://wir2022.wid.world/www-site/uploads/2022/03/WIR2022TablesFigures-Summary.xlsx

```{r}
library(tidyverse)
library(readxl)
```

```{r summary-data, cash = TRUE, eval = FALSE}
url_summary <- "https://wir2022.wid.world/www-site/uploads/2022/03/WIR2022TablesFigures-Summary.xlsx"
download.file(url = url_summary, destfile = "data/WIR2022TablesFigures-Summary.xlsx") 
```

```{r summary-data-sheet, cash = TRUE}
summary_sheets <- excel_sheets("data/WIR2022TablesFigures-Summary.xlsx")
summary_sheets
```

```{r}
df_index <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "Index")
df_index
```
## Data and Charts

### F1: Global income and wealth inequality, 2021

```{r data-f1, cash = TRUE}
df_f1 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F1")
df_f1
```


### F2: The poorest half lags behind: Bottom 50%, middle 40% and top 10% income shares across the world in 2021

```{r data-f2, cash = TRUE}
df_f2 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F2")
df_f2
```

### F3: Top 10/Bottom 50 income gaps across the world, 2021

```{r data-f3, cash = TRUE}
df_f3 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F3")
df_f3
```

### F4: The extreme concentration of capital: wealth inequality across the world, 2021

```{r data-f4, cash = TRUE}
df_f4 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F4")
df_f4
```

### F5: Global income inequality: T10/B50 ratio, 1820-2020

```{r data-f5, cash = TRUE}
df_f5 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F5")
df_f5
```
### F6: Global income inequality: Between vs. Within country inequality (Theil index), 1820-2020

```{r data-f6, cash = TRUE}
df_f6 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F6")
df_f6
```

### F7: Global income inequality, 1820-2020

```{r data-f7, cash = TRUE}
df_f7 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F7")
df_f7
```

### F8: The rise of private versus the decline of public wealth in rich countries, 1970-2020

```{r data-f8, cash = TRUE}
df_f8 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F8")
df_f8
```

### F9: Average annual wealth growth rate, 1995-2021

```{r data-f9, cash = TRUE}
df_f9 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F9")
df_f9
```

### F10: The share of wealth owned by the global 0.1% and billionaires, 2021

```{r data-f10, cash = TRUE}
df_f10 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F10")
df_f10
```

### F11: Top 1% vs bottom 50% wealth shares in Western Europe and the US, 1910-2020

```{r data-f11, cash = TRUE}
df_f11 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F11")
df_f11
```

### F12: Female share in global labor incomes, 1990-2020

```{r data-f12, cash = TRUE}
df_f12 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F12")
df_f12
```
### F13: Female labor income share across the world, 1990-2020

Note that the sheet name of F13 has period at the end. Note that `summary_sheets[30] = ``r summary_sheets[30]` with a period.

```{r data-f13, cash = TRUE}
df_f13 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F13.")
df_f13
```

### F14: Global carbon inequality, 2019. Group contribution to world emissions (%)

Note that the sheet name of F14 has period at the end. Note that `summary_sheets[31] = ``r summary_sheets[31]` with a period.

```{r data-f14, cash = TRUE}
df_f14 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F14.")
df_f14
```

### F15: Per capita emissions acriss the world, 2019

```{r data-f15, cash = TRUE}
df_f15 <- read_excel("data/WIR2022TablesFigures-Summary.xlsx", sheet = "data-F15")
df_f15
```

