---
title: "Mongolia and Japan"
author: "DS-SL"
date: "`r Sys.Date()`"
output:
  html_notebook: 
    number_sections: yes
    toc: true
    toc_float: true
  html_document:
    df_print: paged
---
> We study data on Mongolia and Japan.

# WDI

Here is a comparison of Mongolia and Japan in World Bank data. 

* https://data.worldbank.org/?locations=MN-JP-1W
  - Comparison of data of Mongolia, Japan and the World
  
# Our World in Data

* https://ourworldindata.org

By searching Mongolia, we can find various data.First choose Chart tab and change countries.

## GDP per Capita

For example, GDP per capita measured in constant US-$, which adjusts for inflation.

<iframe src="https://ourworldindata.org/grapher/gdp-per-capita-in-us-dollar-world-bank?tab=chart&country=CHN~MNG~JPN~BRA~RUS~IND" loading="lazy" style="width: 100%; height: 600px; border: 0px none;"></iframe>

## Education

<iframe src="https://ourworldindata.org/grapher/share-of-the-population-with-completed-tertiary-education?tab=chart&country=CHN~BRA~JPN~MNG~RUS~IND" loading="lazy" style="width: 100%; height: 600px; border: 0px none;"></iframe>

## Tourism

International tourism: number of arrivals, 1995 to 2020

<iframe src="https://ourworldindata.org/grapher/international-tourism-number-of-arrivals?tab=chart&country=BRA~MNG~RUS~IND~JPN" style="width: 100%; height: 600px; border: 0px none;"></iframe>


# Education

## Education in Japan


```{r, echo=FALSE}
Sys.setenv(LANG = "en")
library(tidyverse)
library(WDI)
```

```{r, cash=TRUE, eval=FALSE}
url_edu1 <- "https://www.gender.go.jp/about_danjo/whitepaper/r03/zentai/html/honpen/csv/zuhyo01-05-01.csv"
download.file(url_edu1, destfile = "data/edu1.csv")
guess_encoding("data/edu1.csv")
```

```{r, echo=FALSE, cash=TRUE}
df_edu1 <- read_csv("data/edu1.csv", locale = locale(encoding = "Shift-JIS"), skip = 2)
df_edu1
```

```{r}
colnames(df_edu1)
df_edu1$年度
```

```{r}
df_edu0 <- df_edu1
colnames(df_edu0) <- c("year", "highschool_m", "highschool_f", "vocational_m", "vocational_f", "university_m", "university_f", "juniorcollege_f", "gradschool_m", "gradschool_f")
df_edu00 <- df_edu0 %>% mutate(year = 1950:2020, 
                   highschool = (highschool_m + highschool_f)/2,
                   vocational = (vocational_m + vocational_f)/2,
                   university = (university_m + university_f)/2, 
                   juniorcollege = juniorcollege_f,
                   gradschool = (gradschool_m + gradschool_f)/2) 
```

```{r}
df_edu00 %>% select(-(2:10)) %>%
  pivot_longer(!year, names_to = "schools", values_to = "percentage") %>%
  ggplot(aes(x = year, y = percentage, color = schools)) +
  geom_line()
```
```{r}
df_edu00 %>% select(-(2:10)) %>% select(-6) %>%
  pivot_longer(3:5, names_to = "schools", values_to = "percentage") %>%
  mutate(types = factor(schools, levels = c("vocational", "juniorcollege", "university"))) %>%
  ggplot() +
  geom_area(aes(x = year, y = percentage, fill = types)) +
  geom_line(aes(x = year, y = highschool)) + 
  labs(title = "Tertially Education After Highschool", 
       subtitle = "Highschool Graduates in black line", fill = "")
```
```{r}
df_edu00 %>% filter(year >= 1954) %>% select(-(2:10)) %>% 
  pivot_longer(3:5, names_to = "schools", values_to = "percentage") %>%
  mutate(types = factor(schools, levels = c("vocational", "juniorcollege", "university"))) %>%
  pivot_longer(c(highschool, gradschool), names_to = "highgrad", values_to ="value") %>%
  mutate(high_grad = factor(highgrad, levels = c("highschool", "gradschool"))) %>%
  ggplot() +
  geom_area(aes(x = year, y = percentage, fill = types)) +
  geom_line(aes(x = year, y = value, linetype = high_grad)) + 
  scale_x_continuous(breaks = round(seq(1960, 2020, by =10),1)) + 
  scale_y_continuous(breaks = round(seq(0, 100, by =10),1)) + 
  labs(title = "Tertially Education After Highschool", 
       subtitle = "with Highschool Graduates and Graduate School", fill = "", linetype = "")
```
```{r}
library(gridExtra)
df_edu0 %>% mutate(year = 1950:2020) %>%
  filter(year >=1954) %>%
  pivot_longer(!year, names_to = c("schools",".value"), names_sep = "_") %>%
  select(-f) %>% pivot_wider(names_from = schools, values_from = m) %>%
  pivot_longer(3:5, names_to = "schools", values_to = "percentage") %>%
  mutate(types = factor(schools, levels = c("vocational", "juniorcollege", "university"))) %>%
  pivot_longer(c(highschool, gradschool), names_to = "highgrad", values_to ="value") %>%
  mutate(high_grad = factor(highgrad, levels = c("highschool", "gradschool"))) %>%
  ggplot() +
  geom_area(aes(x = year, y = percentage, fill = types)) +
  geom_line(aes(x = year, y = value, linetype = high_grad)) + 
  scale_x_continuous(breaks = round(seq(1960, 2020, by =10),1)) + 
  scale_y_continuous(breaks = round(seq(0, 100, by =10),1)) + 
  theme(legend.position="bottom") +
  labs(title = "Male: Tertially Education After Highschool", 
       subtitle = "with Highschool Graduates and Graduate School", fill = "", linetype = "") -> male
df_edu0 %>% mutate(year = 1950:2020) %>%
  filter(year >=1954) %>%
  pivot_longer(!year, names_to = c("schools",".value"), names_sep = "_") %>%
  select(-m) %>% pivot_wider(names_from = schools, values_from = f) %>%
  pivot_longer(3:5, names_to = "schools", values_to = "percentage") %>%
  mutate(types = factor(schools, levels = c("vocational", "juniorcollege", "university"))) %>%
  pivot_longer(c(highschool, gradschool), names_to = "highgrad", values_to ="value") %>%
  mutate(high_grad = factor(highgrad, levels = c("highschool", "gradschool"))) %>%
  ggplot() +
  geom_area(aes(x = year, y = percentage, fill = types)) +
  geom_line(aes(x = year, y = value, linetype = high_grad)) + 
  scale_x_continuous(breaks = round(seq(1960, 2020, by =10),1)) + 
  scale_y_continuous(breaks = round(seq(0, 100, by =10),1)) + 
  theme(legend.position="bottom") +
  labs(title = "Female: Tertially Education After Highschool", 
       subtitle = "with Highschool Graduates and Graduate School", fill = "", linetype = "") -> female
grid.arrange(male, female, ncol=2)
```


```{r}
df_edu11 <- df_edu1 %>% mutate(年 = 1950:2020, 
                   高等学校 = (`高等学校等（男子）`+ `高等学校等（女子）`)/2,
                   専修学校 = (`専修学校（専門課程，男子）`+ `専修学校（専門課程，女子）`)/2,
                   大学 = (`大学（学部，男子）` + `大学（学部，女子）`)/2, 
                   短期大学 = `短期大学（本科，女子）`,
                   大学院 = (`大学院（男子）` + `大学院（女子）`)/2) %>%
  select(-(1:10))
df_edu11
```
```
df_edu11 %>% 
  pivot_longer(2:6, names_to = "学校", values_to = "進学率") %>%
  ggplot(aes(x = 年, y = 進学率, color = 学校)) +
  geom_line()
```

```{r}
df_edu11 %>% 
  pivot_longer(2:6, names_to = "学校", values_to = "進学率") %>%
  ggplot(aes(x = 年, y = 進学率, color = 学校)) +
  geom_line() +
  theme_gray (base_family = "HiraginoSans-W3") # or base_family = "HiraKakuPro-W3"
```


```{r}
df_edu1 %>% mutate(year = 1950:2020) %>%
  pivot_longer(2:10, names_to = "学校", values_to = "進学率") %>%
  ggplot(aes(x = year, y = 進学率, color = 学校)) +
  geom_line() +
  theme_gray (base_family = "HiraKakuPro-W3") # or base_family = "HiraginoSans-W3"
```
```#{r dev='rag_png'}
df_edu1 %>% mutate(year = 1950:2020) %>%
  pivot_longer(2:10, names_to = "学校", values_to = "進学率") %>%
  ggplot(aes(x = year, y = 進学率, color = 学校)) +
  geom_line()
```
